Eagle: Making multiple-locus association mapping on a genome-wide scale routine

### 2018-08-05 supmaterials.tex
6Aug18 about to add Ari files v1

\begin{table}
\caption{{\bf Implementation and methodology attributes of eight computer programs/packages for genome-wide association mapping.} For the different types of model, 
LMM is linear mixed model.  GLM is generalised linear model., GLMM is generalised linear mixed model, and RF is random forests. 
}
\label{suptabsummary}
\vspace{0.5cm}
\begin{tabular}{lcccccccc} \hline
                                                   Attributes                  & {\bf Eagle}                                 & {\bf bigRR}             & {\bf glmnet}            & {\bf LMM-Lasso}                    & {\bf MLMM} & {\bf r2VIM}      & {\bf FaST-LMM} & {\bf GEMMA} \\  \hline
{\em Implementation}    &         &            &             &                   &            &                &      &      \\ 
\hspace{1mm}  Purpose built$^a$    &   Yes     &    Yes      &  No   &   Yes  &  Yes  &  Yes  & Yes  & Yes          \\ [0.35cm]

@@

{\em Methodology}    &         &            &             &                   &            &                &      &      \\  
\hspace{1mm}  Model                     & LMM   &   &  GLMM &   GLM  & LMM  & RF & LMM   & LMM \\ [0.15cm]

\hspace{1mm} SNPs fitted       &    All/multiple      &    All       &   All        &      All          &  Multiple          &  Multiple              &   Single   &  Single   \\  [0.35cm]

@@

\hspace{1mm} Threshold free$^5$        &    Yes     &  No    &  No         &    No               &     Yes       &  No              &  No   & No      \\  [0.15cm]  \hline

\end{tabular}
{$^a$ \scriptsize{Specifically created for the analysis of GWAS data.}}\\
{$^b$ \scriptsize{Separate programs, one written in Python, the other C++}} \\
{$^c$ \scriptsize{Capacity for additional fixed effects (such as  age, sex, and/or population structure effects) to be included directly in the model.}} \\
\end{table}

\begin{table}
\caption{Some of the key features possessed by Eagle and the other seven computer programs/packages for association mapping}
\label{suptabsummary}

\begin{tabular}{lccccccccc} 
                                &  \multicolumn{9}{c}{Computer Programs/Packages for Association Mapping} \\ \cline{2-10}
                                 & \multicolumn{6}{c}{Multiple-locus}  & & \multicolumn{2}{c}{Single-locus} \\  \cline{2-7}   \cline{9-10}
 Features                 & Eagle  & bigRR & glmnet & LMM-Lasso & MLMM & r2VIM     & & FaST-LMM & GEMMA \\  \hline
Purpose built$^1$    &   Yes     &    Yes      &  No   &  Yes  &  Yes  &  Yes && Yes & Yes           \\ [0.2cm]
Well documented$^2$           & Yes &   No   & Yes   & No     &   Yes     & No          && Yes    &    Yes    \\  [0.2cm]
Simultaneous   &    Yes     &    Yes        &   Yes          &      Yes             &  No          &  No              &&   No   &  No     \\  
fitting of SNPs     &         &            &             &                   &            &                &&      &      \\  [0.2cm]
Additional fixed effects$^3$          &   Yes   &      Yes      &     Yes    &  No                 &      Yes      &      Yes          &&      Yes & Yes     \\   [0.2cm]
Data larger than RAM$^4$                   &   Yes    &      No      & No          &  No    &  No    &   No     && Yes      & No    \\  [0.2cm]
Threshold free$^5$        &    Yes     &  No    &  No         &    No               &     Yes       &  No              &&  No   & No      \\  [0.2cm]
Informative error checking           &  Yes      &     No        &      No     &           No        &      No       &         No       && Yes  & No \\ \hline

\end{tabular}
{$^1$ \scriptsize{Specifically created for the analysis of GWAS data.}}\\
{$^2$ \scriptsize{More than just a readme file or comments in an example file. Programs/packages with a tick had a detailed user manual.}}\\
{$^3$ \scriptsize{Ability to handle additional fixed effects such as  age, sex, and/or population structure effects.}} \\
{$^4$ \scriptsize{Able to deal with data larger than the memory capacity of the computer.}} \\
{$^5$ \scriptsize{Results reported as the set of SNP closest to the genes influencing a trait. No need to construct thresholds to determine 
significance of the findings.}}\\
{$^6$  \scriptsize{All the programs terminated on errors. However, not all the programs informed the user of the cause and how to fix the errors.}}\\
\end{table}

>>>>

\begin{table}
\caption{Implementation and methodology attributes of eight computer programs/packages for genome-wide association mapping.  }
\label{suptabsummary}
\vspace{0.5cm}
\begin{tabular}{lcccccccc} \hline
                                                   Attributes                  & {\bf Eagle}                                 & {\bf bigRR}             & {\bf glmnet}            & {\bf LMM-Lasso}                    & {\bf MLMM} & {\bf r2VIM}      & {\bf FaST-LMM} & {\bf GEMMA} \\  \hline
{\em Implementation}    &         &            &             &                   &            &                &      &      \\ [0.35cm]
\hspace{1mm}  Purpose built$^a$    &   Yes     &    Yes      &  No   &   Yes  &  Yes  &  Yes  & Yes  & Yes          \\ [0.35cm]

@@

{\em Methodology}    &         &            &             &                   &            &                &      &      \\  [0.35cm]
\hspace{1mm}  Model $^d$                    & LMM   &   &  GLMM &   GLM  & LMM  & RF & LMM   & LMM \\ [0.15cm]

\hspace{1mm} SNPs fitted $^e$      &    All/multiple      &    All       &   All        &      All          &  Multiple          &  Multiple              &   Single   &  Single   \\  [0.35cm]

@@

\hspace{1mm} Threshold free      &    Yes     &  No    &  No         &    No               &     Yes       &  No              &  No   & No      \\  [0.15cm]  \hline

\end{tabular}
{$^a$ \scriptsize{Specifically created for the analysis of GWAS data.}}\\
{$^b$ \scriptsize{Separate programs, one written in Python, the other C++}} \\
{$^c$ \scriptsize{Capacity for additional fixed effects (such as  age, sex, and/or population structure effects) to be included directly in the model.}} \\
{$^d$ \scriptsize{For the different types of model, 
LMM is linear mixed model.  GLM is generalised linear model., GLMM is generalised linear mixed model, and RF is random forests.}} \\
{$^e$ \scriptsize{Association is assessed a SNP at a time (single), for multiple SNPs (multiple), or for all SNPs (all). Eagle fits all SNPs but also identifies multiple SNPs (All/multiple) in association with the trait.} } \\
\end{table}
